Shannon diversity

### 2021-02-23 analysis/reports/manuscript_main.Rmd
jk results

  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(skew_percentile_excl)) +
    geom_histogram(bins = 100) +
    geom_vline(xintercept = 95, color = "red") +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Skewness") +
    xlab("") +
    ylab(""),# +
  #  xlab("Percentile rank of observed value relative to feasible set") +
    #ylab("Number of communities") ,

  ggplot(filter(all_di, simpson_unique > 20), aes(simpson_percentile)) + 
    geom_histogram(bins = 100) +
    geom_vline(xintercept = 5, color = "red") +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Evenness") + 
    xlab("") +
    ylab("")#+
    #xlab("Percentile rank of observed value relative to feasible set") +
  #  ylab("Number of communities")
), ncol = 2,
left = "Number of communities",
bottom = "Percentile rank of observed value relative to feasible set")

plot(fig_2)

@@

fig_3 <- gridExtra::grid.arrange(grobs = list(
  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x= skew_95_ratio_1t)) +
    geom_histogram() +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
    xlab("") +
    ylab("") +
    ggtitle("Skewness") +
    xlim(0, 1),

  ggplot(filter(all_di, simpson_unique > 20), aes(x = simpson_95_ratio_1t)) +
    geom_histogram() +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
    xlab("") +
    ylab("") +
    ggtitle("Evenness") +
    xlim(0, 1)
), ncol = 2,
left = "Number of communities", 
bottom = "Breadth index (ranges 0-1, with 1 being very broad)")

@@

simpson_ks <- filter(sub_di, simpson_unique > 20) %>%
  select(simpson_95_ratio_1t, Dataset, simpson_percentile, s0, n0) %>% 
  group_by(Dataset, s0, n0) %>%
  mutate(pairing = dplyr::row_number()) %>%
  ungroup() %>%
  tidyr::pivot_wider(id_cols = c(s0, n0, pairing), names_from = Dataset, values_from = c(simpson_95_ratio_1t, simpson_percentile))

@@

skewness_ks <- filter(sub_di, skew_unique > 20) %>%
  select(skew_95_ratio_1t, Dataset, skew_percentile, s0, n0) %>% 
  group_by(Dataset, s0, n0) %>%
  mutate(pairing = dplyr::row_number()) %>%
  ungroup() %>%
  tidyr::pivot_wider(id_cols = c(s0, n0, pairing), names_from = Dataset, values_from = c(skew_95_ratio_1t, skew_percentile))

@@

fig_4 <- gridExtra::grid.arrange(grobs = list(
  ggplot(filter(sub_di, skew_unique > 20), aes(skew_95_ratio_1t)) +
    geom_histogram()+
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y")  +
    xlab("Breadth index") +
    ylab("Number of communities") +
    ggtitle("Breadth index", subtitle = "Skewness"),

  ggplot(filter(sub_di, simpson_unique > 20), aes(simpson_95_ratio_1t)) +
    geom_histogram()+
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y")  +
    xlab("Breadth index") +
    ylab("") +
    ggtitle("", subtitle = "Evenness"),

  ggplot(filter(sub_di, skew_unique > 20), aes(skew_percentile_excl)) +
    geom_histogram()+
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y")  +
    xlab("Percentile rank") +
    ylab("Number of communities") +
    ggtitle("Percentile rank", subtitle = "Skewness"),

  ggplot(filter(sub_di, simpson_unique > 20), aes(simpson_percentile)) +
    geom_histogram()+
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y")  +
    xlab("Percentile rank") +
    ylab("")+
    ggtitle("", subtitle = "Evenness")), ncol = 2)

@@

```{r}
pdf("figure_1.pdf", title = "Figure 1")
plot(fig_1)
dev.off()

pdf("figure_2.pdf", title = "Figure 2")
 plot(fig_2)
 dev.off()

pdf("figure_3.pdf", title = "Figure 3")
plot(fig_3)
dev.off()

pdf("figure_4.pdf", title = "Figure 4")
 plot(fig_4)
dev.off()
```

>>>>

  ggplot(filter(all_di, s0 > 2, nparts > 20), aes(skew_percentile_excl)) +
    geom_histogram(bins = 100) +
    geom_vline(xintercept = 95, color = "red") +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Skewness") +
    xlab("") +
    ylab(""),# +
  #  xlab("Percentile rank of observed value relative to feasible set") +
    #ylab("Number of communities") ,

  ggplot(filter(all_di, nparts > 20), aes(simpson_percentile)) + 
    geom_histogram(bins = 100) +
    geom_vline(xintercept = 5, color = "red") +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Evenness") + 
    xlab("") +
    ylab("")#+
    #xlab("Percentile rank of observed value relative to feasible set") +
  #  ylab("Number of communities")
), ncol = 2,
top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))

@@

fig_3 <- gridExtra::grid.arrange(grobs = list(
  ggplot(filter(all_di, s0 > 2, nparts > 20), aes(x= skew_95_ratio_1t)) +
    geom_histogram() +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
    xlab("") +
    ylab("") +
    ggtitle("Skewness") +
    xlim(0, 1),

  ggplot(filter(all_di, nparts > 20), aes(x = simpson_95_ratio_1t)) +
    geom_histogram() +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
    xlab("") +
    ylab("") +
    ggtitle("Evenness") +
    xlim(0, 1)
), ncol = 2,
top = textGrob("Figure 3", gp = gpar(fill = "white")),
left = "Number of communities", 
bottom = "Breadth index (ranges 0-1, with 1 being very broad)")

@@

simpson_ks <- filter(sub_di, nparts > 20) %>%
  select(simpson_95_ratio_1t, Dataset, simpson_percentile, s0, n0) %>% 
  group_by(Dataset, s0, n0) %>%
  mutate(pairing = dplyr::row_number()) %>%
  ungroup() %>%
  tidyr::pivot_wider(id_cols = c(s0, n0, pairing), names_from = Dataset, values_from = c(simpson_95_ratio_1t, simpson_percentile))

@@

skewness_ks <- filter(sub_di, nparts > 20) %>%
  select(skew_95_ratio_1t, Dataset, skew_percentile, s0, n0) %>% 
  group_by(Dataset, s0, n0) %>%
  mutate(pairing = dplyr::row_number()) %>%
  ungroup() %>%
  tidyr::pivot_wider(id_cols = c(s0, n0, pairing), names_from = Dataset, values_from = c(skew_95_ratio_1t, skew_percentile))

@@

fig_4 <- gridExtra::grid.arrange(grobs = list(
  ggplot(filter(sub_di, nparts > 20), aes(skew_95_ratio_1t)) +
    geom_histogram()+
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y")  +
    xlab("Breadth index") +
    ylab("Number of communities") +
    ggtitle("Breadth index", subtitle = "Skewness"),

  ggplot(filter(sub_di, nparts > 20), aes(simpson_95_ratio_1t)) +
    geom_histogram()+
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y")  +
    xlab("Breadth index") +
    ylab("") +
    ggtitle("", subtitle = "Evenness"),

  ggplot(filter(sub_di, nparts > 20), aes(skew_percentile_excl)) +
    geom_histogram()+
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y")  +
    xlab("Percentile rank") +
    ylab("Number of communities") +
    ggtitle("Percentile rank", subtitle = "Skewness"),

  ggplot(filter(sub_di, nparts > 20), aes(simpson_percentile)) +
    geom_histogram()+
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y")  +
    xlab("Percentile rank") +
    ylab("")+
    ggtitle("", subtitle = "Evenness")), ncol = 2, top = textGrob("Figure 4", gp = gpar(fill = "white")))

@@

```{r}
pdf("figure_1.pdf", title = "Figure 1", bg = "white", paper = "letter", width = 6.5, height = 6.5)
gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 1", gp = gpar(fill = "white")))
dev.off()

pdf("figure_2.pdf", title = "Figure 2", bg = "white", paper = "letter", width = 6.5, height = 6.5)
 gridExtra::grid.arrange(grobs = list(

  ggplot(filter(all_di, s0 > 2, nparts > 20), aes(skew_percentile_excl)) +
    geom_histogram(bins = 100) +
    geom_vline(xintercept = 95, color = "red") +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Skewness") +
    xlab("") +
    ylab(""),# +
  #  xlab("Percentile rank of observed value relative to feasible set") +
    #ylab("Number of communities") ,

  ggplot(filter(all_di, nparts > 20), aes(simpson_percentile)) + 
    geom_histogram(bins = 100) +
    geom_vline(xintercept = 5, color = "red") +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Evenness") + 
    xlab("") +
    ylab("")#+
    #xlab("Percentile rank of observed value relative to feasible set") +
  #  ylab("Number of communities")
), ncol = 2,
top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
 dev.off()

pdf("figure_3.pdf", title = "Figure 3", bg = "white", paper = "letter", width = 6.5, height = 6.5)
gridExtra::grid.arrange(grobs = list(
  ggplot(filter(all_di, s0 > 2, nparts > 20), aes(x= skew_95_ratio_1t)) +
    geom_histogram() +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
    xlab("") +
    ylab("") +
    ggtitle("Skewness") +
    xlim(0, 1),

  ggplot(filter(all_di, nparts > 20), aes(x = simpson_95_ratio_1t)) +
    geom_histogram() +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
    xlab("") +
    ylab("") +
    ggtitle("Evenness") +
    xlim(0, 1)
), ncol = 2,
top = textGrob("Figure 3", gp = gpar(fill = "white")),
left = "Number of communities", 
bottom = "Breadth index (ranges 0-1, with 1 being very broad)")

dev.off()

pdf("figure_4.pdf", title = "Figure 4", bg = "white", paper = "letter", width = 6.5, height = 6.5)
 gridExtra::grid.arrange(grobs = list(
  ggplot(filter(sub_di, nparts > 20), aes(skew_95_ratio_1t)) +
    geom_histogram()+
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y")  +
    xlab("Breadth index") +
    ylab("Number of communities") +
    ggtitle("Breadth index", subtitle = "Skewness"),

  ggplot(filter(sub_di, nparts > 20), aes(simpson_95_ratio_1t)) +
    geom_histogram()+
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y")  +
    xlab("Breadth index") +
    ylab("") +
    ggtitle("", subtitle = "Evenness"),

  ggplot(filter(sub_di, nparts > 20), aes(skew_percentile_excl)) +
    geom_histogram()+
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y")  +
    xlab("Percentile rank") +
    ylab("Number of communities") +
    ggtitle("Percentile rank", subtitle = "Skewness"),

  ggplot(filter(sub_di, nparts > 20), aes(simpson_percentile)) +
    geom_histogram()+
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y")  +
    xlab("Percentile rank") +
    ylab("")+
    ggtitle("", subtitle = "Evenness")), ncol = 2, top = textGrob("Figure 4", gp = gpar(fill = "white")))
dev.off()
```

### 2021-02-23 analysis/rev_prototyping/jacknife_results.Rmd
jk results

all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)

jk_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv"))

jk_di <- jk_di %>%
  group_by_all() %>%
  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
  ungroup() %>%
  select(dat, site, site_source, s0, n0, skew_percentile_excl, simpson_percentile, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)

@@

all_di_actual <- all_di %>%
    filter(!singletons) %>%
  mutate(site_source = as.character(site)) %>%
  select(dat, site_source, s0, n0, skew_percentile_excl, simpson_percentile, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)

colnames(all_di_actual)[ 3:19] <- paste0(colnames(all_di_actual)[ 3:19], "_actual")

@@

jk_di_mean_results <- jk_di_mean_results %>%
  mutate(skew_actual_sig = skew_percentile_excl_actual > 95,
         skew_sig = skew_percentile_excl > 95) %>%
  mutate(skew_change = paste0("actual", skew_actual_sig, "_jk", skew_sig))

@@

```{r}
ggplot(filter(jk_di_mean_results, s0 > 2), aes(skew_percentile_excl)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

ggplot(filter(jk_di_mean_results, s0 > 2), aes(skew_percentile_excl_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

jk_di_mean_results  %>% 
 filter(s0 > 2) %>%
  group_by(dat) %>%
  summarize(prop_skew_high_jk = mean(skew_percentile_excl > 95),
            prop_skew_high_raw = mean(skew_percentile_excl_actual > 95),
            nsites_included = dplyr::n())
```

@@

```{r}
ggplot(filter(jk_di_mean_results), aes(simpson_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 5)

ggplot(filter(jk_di_mean_results), aes(simpson_percentile_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 5)

jk_di_mean_results  %>% 
  group_by(dat) %>%
  summarize(prop_simpson_high_jk = mean(simpson_percentile < 5),
            prop_simpson_high_raw = mean(simpson_percentile_actual < 5),
            nsites_included = dplyr::n())

@@

```{r}
ggplot(filter(jk_di_mean_results), aes(shannon_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 5)

ggplot(filter(jk_di_mean_results), aes(shannon_percentile_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 5)

jk_di_mean_results  %>% 
  group_by(dat) %>%
  summarize(prop_shannon_high_jk = mean(shannon_percentile < 5),
            prop_shannon_high_raw = mean(shannon_percentile_actual < 5),
            nsites_included = dplyr::n())

@@

```{r}
ggplot(filter(jk_di_mean_results), aes(mean_po_comparison_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

ggplot(filter(jk_di_mean_results), aes(mean_po_comparison_percentile_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

jk_di_mean_results  %>% 
  group_by(dat) %>%
  summarize(prop_mean_po_comparison_high_jk = mean(mean_po_comparison_percentile > 95),
            prop_mean_po_comparison_high_raw = mean(mean_po_comparison_percentile_actual > 95),
            nsites_included = dplyr::n())

@@

## Nsingletons

```{r}
ggplot(filter(jk_di_mean_results), aes(nsingletons_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

ggplot(filter(jk_di_mean_results), aes(nsingletons_percentile_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

jk_di_mean_results  %>% 
  group_by(dat) %>%
  summarize(prop_nsingletons_high_jk = mean(nsingletons_percentile > 95),
            prop_nsingletons_high_raw = mean(nsingletons_percentile_actual > 95),
            nsites_included = dplyr::n())

@@

```{r}
ggplot(filter(jk_di_mean_results), aes(nsingletons_percentile_excl)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

ggplot(filter(jk_di_mean_results), aes(nsingletons_percentile_excl_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

jk_di_mean_results  %>% 
  group_by(dat) %>%
  summarize(prop_nsingletons_high_jk = mean(nsingletons_percentile_excl > 95),
            prop_nsingletons_high_raw = mean(nsingletons_percentile_excl_actual > 95),
            nsites_included = dplyr::n())

@@

>>>>

all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F) %>%
  filter(n0 != s0,
         s0 != 1,
         !singletons,
         n0 != (s0 + 1))

jk_di_full <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv"))

jk_di <- jk_di_full %>%
  group_by_all() %>%
  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
  ungroup() %>%
  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingeltons_median, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)

@@

all_di_actual <- all_di %>%
  filter(!singletons) %>%
  mutate(site_source = as.character(site)) %>%
  select(dat, site_source, s0, n0, skew_percentile_excl, skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons,nsingeltons_median,  nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)

colnames(all_di_actual)[ 3:ncol(all_di_actual)] <- paste0(colnames(all_di_actual)[3:ncol(all_di_actual)], "_actual")

@@

jk_di_mean_results <- jk_di_mean_results %>%
  mutate(skew_actual_sig = skew_percentile_excl_actual > 95,
         skew_sig = skew_percentile_excl > 95) %>%
  mutate(skew_change = paste0("actual", skew_actual_sig, "_jk", skew_sig)) %>%
  filter(nparts > 20)

@@

```{r}
ggplot(filter(jk_di_mean_results, s0 > 2, nparts > 20), aes(skew_percentile_excl)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

ggplot(filter(jk_di_mean_results, s0 > 2, nparts > 20), aes(skew_percentile_excl_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

jk_di_mean_results  %>% 
  filter(s0 > 2, nparts > 20) %>%
  group_by(dat) %>%
  summarize(prop_skew_high_jk = mean(skew_percentile_excl > 95),
            prop_skew_high_raw = mean(skew_percentile_excl_actual > 95),
            prop_skew_low_jk = mean(skew_percentile < 5),
            prop_skew_low_raw = mean(skew_percentile_actual < 5),
            nsites_included = dplyr::n())
```

@@

```{r}
ggplot(filter(jk_di_mean_results, nparts > 20), aes(simpson_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 5)

ggplot(filter(jk_di_mean_results, nparts > 20), aes(simpson_percentile_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 5)

jk_di_mean_results  %>% 
  group_by(dat) %>%
  filter(nparts > 20) %>%
  summarize(prop_simpson_high_jk = mean(simpson_percentile_excl > 95),
            prop_simpson_high_raw = mean(simpson_percentile_excl_actual > 95),
            prop_simpson_low_jk = mean(simpson_percentile< 5),
            prop_simpson_low_raw = mean(simpson_percentile_actual < 5),
            nsites_included = dplyr::n())

@@

```{r}
ggplot(filter(jk_di_mean_results, nparts > 20), aes(shannon_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 5)

ggplot(filter(jk_di_mean_results, nparts > 20), aes(shannon_percentile_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 5)

jk_di_mean_results  %>% 
  group_by(dat) %>%
  filter(nparts > 20) %>%
  summarize(prop_shannon_high_jk = mean(shannon_percentile > 95),
            prop_shannon_high_raw = mean(shannon_percentile_actual > 95),
            prop_shannon_low_jk = mean(shannon_percentile< 5),
            prop_shannon_low_raw = mean(shannon_percentile_actual < 5),
            nsites_included = dplyr::n())

@@

```{r}
ggplot(filter(jk_di_mean_results, nparts > 20), aes(mean_po_comparison_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

ggplot(filter(jk_di_mean_results, nparts > 20), aes(mean_po_comparison_percentile_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

jk_di_mean_results  %>% 
  group_by(dat) %>%
  filter(nparts > 20) %>%
  summarize(prop_mean_po_comparison_high_jk = mean(mean_po_comparison_percentile > 95),
            prop_mean_po_comparison_high_raw = mean(mean_po_comparison_percentile_actual > 95),
            nsites_included = dplyr::n())

@@

<!-- ## Nsingletons -->

<!-- ```{r} -->
<!-- ggplot(filter(jk_di_mean_results, nparts > 20), aes(nsingletons_percentile_excl)) + -->
<!--   geom_histogram(bins = 100) + -->
<!--   facet_wrap(vars(dat), scales = "free_y", ncol = 1) + -->
<!--   geom_vline(xintercept = 95) -->

<!-- ggplot(filter(jk_di_mean_results, nparts > 20), aes(nsingletons_percentile_actual)) + -->
<!--   geom_histogram(bins = 100) + -->
<!--   facet_wrap(vars(dat), scales = "free_y", ncol = 1) + -->
<!--   geom_vline(xintercept = 95) -->

<!-- jk_di_mean_results  %>%  -->
<!--   group_by(dat) %>% -->
<!--   summarize(prop_nsingletons_high_jk = mean(nsingletons_percentile > 95), -->
<!--             prop_nsingletons_high_raw = mean(nsingletons_percentile_actual > 95), -->
<!--             nsites_included = dplyr::n()) -->

Visualization and analysis of nsingletons has a little more nuance than the others, because there are often relatively few values for nsingletons at all. 80% of sites have fewer than 20 singletons as the 95th percentile, which is just a rough way of saying that a **lot** of these are going to be sensitive to whether you define the percentiles as > or >=.

In general the strict > percentile will give you an (appropriately) conservative estimate of how many are extraordinarily **high** and the >= will give you an appropriate estimate of how many are unusually **low**. For most metrics it doesn't really matter, writ large, which you use, because ties are rare. For this one, you get large numbers of sites where a lot of values are = to the observed values, and the >= decision will therefore give you a jump of a lot of percentile scores.

For the "proportions high/low" calculations, we use *the > percentile for high* and *the >= percentile for low*. For visualization, because we are interested in both unusually high and unusually low scores, we can't just pick one or the other. The histogram using >= is reliable at the high end but has a misleading spike at 0, and vice versa. I am making these plots using the *mean*, which doesn't have the misleading spikes at the extremes but does smear things out a little bit.

```{r, fig.dim = c(5,5)}

jk_di_mean_results <- jk_di_mean_results %>%
  group_by_all() %>%
  mutate(singletons_percentile_jump = nsingletons_percentile - nsingletons_percentile_excl,
         singletons_percentile_jump_actual = nsingletons_percentile_actual - nsingletons_percentile_excl_actual,
         nsingletons_percentile_mean = sum(nsingletons_percentile, nsingletons_percentile_excl) / 2,
         nsingletons_percentile_mean_actual = sum(nsingletons_percentile_actual, nsingletons_percentile_excl_actual)/2) %>%
  ungroup()

@@

```{r}
ggplot(filter(jk_di_mean_results, nparts > 20), aes(nsingletons_percentile_mean)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

ggplot(filter(jk_di_mean_results, nparts > 20), aes(nsingletons_percentile_mean_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

jk_di_mean_results  %>% 
  group_by(dat) %>%
  filter(nparts > 20) %>%
  summarize(prop_nsingletons_high_jk = mean(nsingletons_percentile_excl > 95),
            prop_nsingletons_high_raw = mean(nsingletons_percentile_excl_actual > 95),
         #   prop_nsingletons_mean_high_raw = mean(nsingletons_percentile_mean_actual > 95),
      #      prop_nsingletons_mean_high_jk = mean(nsingletons_percentile_mean > 95),
            prop_nsingletons_low_jk = mean(nsingletons_percentile < 5),
            prop_nsingletons_low_raw = mean(nsingletons_percentile_actual  < 5),
            nsites_included = dplyr::n())

@@

<!-- ```{r, fig.dim = c(6,6)} -->

<!-- jk_di_mean_results <- jk_di_mean_results %>% -->
<!--  #select(-singletons_percentile_excl_high_insig, -singletons_percentile_low_insig) -->
<!--   group_by_all() %>% -->
<!--   mutate(prop_singletons = nsingletons / s0, -->
<!--          prop_singletons_actual = nsingletons_actual / s0, -->
<!--          singletons_percentile_high_change = paste0("actual", (nsingletons_percentile_excl_actual > 95), "_jk", (nsingletons_percentile_excl > 95)), -->
<!--          singletons_percentile_low_change = paste0("actual", (nsingletons_percentile_actual <5), "_jk", (nsingletons_percentile < 5))) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(prop_singletons_change = prop_singletons - prop_singletons_actual) -->

<!-- ggplot(jk_di_mean_results, aes(prop_singletons_actual, prop_singletons, color =singletons_percentile_high_change)) + geom_point() + geom_line(aes(prop_singletons_actual,prop_singletons_actual), inherit.aes = F) -->

<!-- ggplot(jk_di_mean_results, aes(nsingletons_actual, nsingletons,color = singletons_percentile_high_change)) + geom_point() + geom_line(aes(nsingletons_actual,nsingletons_actual), inherit.aes = F) +facet_wrap(vars(dat), scales = "free") + theme(legend.position = "top") -->

<!-- ggplot(jk_di_mean_results, aes(s0,n0, color =  -->
<!-- ggplot(jk_di_mean_results, aes(nsingletons_actual, nsingletons,color = singletons_percentile_high_change)) + geom_point() + geom_line(aes(nsingletons_actual,nsingletons_actual), inherit.aes = F) +facet_wrap(vars(dat), scales = "free") + theme(legend.position = "top") -->
<!-- )) + geom_point() +scale_x_log10() +scale_y_log10() + -->
<!--   facet_wrap(vars(dat), scales = "free") + -->
<!--   theme(legend.position = "top") -->

<!-- ggplot(jk_di_mean_results, aes(s0,n0, color = singletons_percentile_low_change)) + geom_point() +scale_x_log10() +scale_y_log10()+ -->
<!--   facet_wrap(vars(dat), scales = "free") + -->
<!--   theme(legend.position = "top") -->

<!-- ggplot(jk_di_mean_results, aes(n0/s0, nsingletons_percentile_excl, color = singletons_percentile_high_change)) + geom_point()+ -->
<!--   facet_wrap(vars(dat), scales = "free") + -->
<!--   theme(legend.position = "top") -->
<!-- ``` -->

### 2021-02-23 analysis/rev_prototyping/nsingletons.Rmd
jk results

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 != s0,
         s0 != 1,
         !singletons,
         n0 != (s0 + 1)) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset))

@@

ggplot(all_di, aes(nsingletons_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat, singletons), scales = "free_y") +
  xlim(0, 100)

ggplot(all_di, aes(nsingletons_percentile_excl)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat, singletons), scales = "free_y") +
  xlim(0, 100)

>>>>

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 != s0,
         s0 != 1,
         !singletons,
         n0 != (s0 + 1)) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
  filter(nparts > 20)

@@

ggplot(all_di, aes(nsingletons_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat, singletons), scales = "free_y")

ggplot(all_di, aes(nsingletons_percentile_excl)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat, singletons), scales = "free_y")
